New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-08-20 experiment.tex
Changes to the last experiment

The second question is whether a coupling method would more consistently provide true answers. In Figure \ref{fig:score} we show the difference of accuracies of the classification models $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ after ten-fold change of priors. Again we can see, that there is no uniform advantage to either method.
% Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question

@@

>>>>

@@

The second question is whether a coupling method would more consistently provide true answers. In Figure \ref{fig:score} we show the difference of accuracies of the classification models $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ after ten-fold change of priors for 'mnist' dataset. Again we can see, that there is no uniform advantage to either method.
% Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question
